Exploring Disparate Data: Part 1

### 2024-11-04 A3-Pt1.Rmd
Update A3-Pt1.Rmd

```{r}
ice_extent_yearly <- ice_extent_daily |>
    # YOUR CODE HERE
    group_by(year, region) |>
    summarize(
        min = min(ice_extent, na.rm = TRUE),
        max = max(ice_extent, na.rm = TRUE)
    ) |>
    pivot_longer(
        cols = c("min", "max"),
        names_to = "name",
        values_to = "value"
    )

ice_extent_yearly
```

@@

```{r sea_ice_parquet, error=TRUE}
# YOUR CODE HERE
```

>>>>

```{r}
ice_extent_yearly <- ice_extent_daily |>
    # YOUR CODE HERE
    group_by(year, region) |>
    summarize(
        min = min(ice_extent, na.rm = TRUE),
        max = max(ice_extent, na.rm = TRUE),
        .groups = "drop"
    ) |>
    pivot_longer(
        cols = c("min", "max"),
        names_to = "name",
        values_to = "value"
    )
ice_extent_yearly
```

@@

```{r sea_ice_parquet, error=TRUE}
# YOUR CODE HERE
write_parquet(ice_extent_yearly, "ice_extent_yearly.parquet")
```
